---
title: "Survey of dress codes"
output: html_document
date: "2025-03-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(plotly)
```



```{r load, include = FALSE}
survey <- read.csv2("survey1.csv")
summary(survey)
```

## Plots
### Men's attire
Plenty of orchestras still use bow tie. Some have moved to no specific tie requirement.

__Compare:__ Hover to show frequency.

```{r ties, echo=FALSE}
p <- ggplot(data = survey) +
  geom_bar(mapping = aes(x=tie))
ggplotly(p) %>% layout(xaxis=list(fixedrange=TRUE)) %>% layout(yaxis=list(fixedrange=TRUE))
```
Tail coat and vest is still common.

__Compare:__ Hover to show frequency.
```{r jacket, echo=FALSE}
p <- ggplot(data = survey) +
  geom_bar(mapping = aes(x=jacket))
ggplotly(p) %>% layout(xaxis=list(fixedrange=TRUE)) %>% layout(yaxis=list(fixedrange=TRUE))
```

### Women's attire
Sleeve, neck and attire length vary on different regions.

__Guess the orchestra__: Hover to show orchestra name.

__Compare regions__: Click to toggle, double-click to isolate.
```{r surveyplot, include = FALSE}
ggplot(data = survey,
       mapping = aes(x=sleeve, y=neck, color = region)) +
  geom_point(position = 'jitter')
```

```{r surveyplot2, include = FALSE}
ggplot(data = survey,
       mapping = aes(x=sleeve, y=length, color = region)) +
  geom_point(position = 'jitter') +
  xlim(0, 105) +  # Ensures x-axis starts at 0, NA allows automatic upper limit
  ylim(0, 105)    # Ensures y-axis starts at 0
```

Hover to show orchestra name, double-click on region to isolate region, click to toggle

```{r interactive, echo=FALSE}
p <- ggplot(data = survey,
       mapping = aes(x=sleeve, y=neck, color = region, text = long)) +
  geom_point(position = 'jitter') +
  xlim(-5, 105) +  # Ensures x-axis starts at 0, NA allows automatic upper limit
  ylim(-5, 105)    # Ensures y-axis starts at 0
ggplotly(p, tooltip = "text") %>% layout(xaxis=list(fixedrange=TRUE)) %>% layout(yaxis=list(fixedrange=TRUE))
```

```{r interactive2, echo=FALSE}
p <- ggplot(data = survey,
       mapping = aes(x=sleeve, y=length, color = region, text = long)) +
  geom_point(position = 'jitter')  +
  xlim(-5, 105) +  # Ensures x-axis starts at 0, NA allows automatic upper limit
  ylim(105, -5)    # Ensures y-axis starts at 0
ggplotly(p, tooltip = "text") %>% layout(xaxis=list(fixedrange=TRUE)) %>% layout(yaxis=list(fixedrange=TRUE))
```


